---
title: "Mood Boost Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: paper
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Sidebar {.sidebar}
==================

ABSTRACT

Highlighted: 

- Total variance explained
- Most influencial variable 

Results
=======

Column {data-width=650}
-----------------------------------------------------------------------

### Correlations between the spotify vars and self esteem {data-height=350}
A plot of of the spotify variables (e.g. mode and dancebility) correlated to the self-esteem scores. 

```{r}

```

### Qualitative results summarized {data-height=650}
Does music alter self-esteem?
What music alters self-esteem?

Column {data-width=350}
-----------------------------------------------------------------------

### Correlations over socio-demogrphic variable {data-height=700}
like left, but then ranged over different values of a sociodemographic variable (probably musical sophistication)

```{r}

```

### Intercorrelations between explaining variables {data-height=300}
An intercorralation plot between both the spotify variables and the socio-demographic variables.

```{r}

```

Background 
==========
